---
title: "Building a {distill} website"
description: "How I built this site using {distill}"
author:
  - name: Kenji
date: 2022-07-12
categories:
    - tutorial
    - R
    - distill
preview: distill-logo.jpeg
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 2
---

## Tools

- OS: Ubuntu 22.04
- R (Version 4.2.1)
- [Rstudio](https://www.rstudio.com/)
- [Github](https://github.com/)
- [Netlify](https://www.netlify.com/)
- Packages: Distill; Usethis

## Instructions

### 1 - Install distill package

```{r eval=FALSE}

install.packages("distill")

```

### 2 - Create new project

```{r eval=FALSE}

distill::create_blog(dir = "directory", title = "Blog Name")

```


### 3 - Structure  

`site.yml`: website configuration file.  

`index.Rmd`: blog home page (Rmarkdown).    

`about.Rmd`: about page (Rmarkdown).   

`_posts`: folder with raw Rmarkdown posts.  

`_site`: folder where the built site lives as final HTML and other supporting files.  


### 4 - distill functions

- `create_post("name post")`

```{r eval=FALSE}

distill::create_post(
    title,
    author = "auto",
    slug = "auto", # generates a website slug (URL)
    date_prefix = TRUE, # add like 2022-07-12-blog-post
    draft = FALSE, #this prevents the post from being included in the site build until you turn it to FALSE
    edit = interactive()
)

```


- `create_theme("name theme")`: Modify css blog theme.  

### 5 - Git/Github

- Add git locally, run `usethis::use_git()` command.  
- Connect Github to existing project via Rstudio, run `usethis::use_github()` command.  
- Commit and push.  

### 6 - Netlify

- Import from github: deploy website.  
- Change domain (Example : https://gyoza-restaurant.netlify.app/).  
- Set the Publish directory to `_site` 

### 7 - Basic blog workflow

- Create new blog post in RStudio: `distill::create_post()`  
- Knit new blog post: `ctrl + shift + k`
- Commit and push: integration between RStudio and Github  

### 8 - Styles (CSS)

- [X] Add RSS: index.xml  
- [X] Add social media icons  
- [X] Modify fonts/colors/bar: New css theme  
- [X] Add Categories  


## Example distill blogs

- [Before I Sleep](https://milesmcbain.xyz/)
- [The Mockup](https://themockup.blog)
- [Taras Kaduk](https://taraskaduk.com/)  
- [Open Source Football](https://www.opensourcefootball.com/)  

## Links

- [Rstudio distill blog](https://rstudio.github.io/distill/)

- [Lisa Lendway - Youtube tutorial](https://www.youtube.com/watch?v=Fm3bsYCilEU)  

- [Building a blog with distill - Thomas Mock](https://themockup.blog/posts/2020-08-01-building-a-blog-with-distill/)