---
title: "Building a {distill} website"
description: "How I built this site using {distill}"
author:
  - name: Kenji
date: 2022-07-12
categories:
    - tutorial
    - R
    - distill
preview: distill-logo.jpeg
output:
  distill::distill_article:
    self_contained: false

---

## Tools

- Opearational system: Ubuntu 20.04
- R (Version 4.2.1)
- Rstudio (IDE)
- Github
- Netlify

## Instructions

**1. Install distill package**

```{r eval=FALSE}

install.packages("distill")

```

**2. Create new project**

```{r eval=FALSE}

distill::create_blog(dir = "directory", title = "Blog Name")

```


**3. Structure**  

`site.yml`: website configuration file  

- [X] Add RSS: index.xml  
- [X] Add social media icons  
- [X] Modify fonts/colors/bar: new css theme  
- [X] Add Categories  

`index.Rmd`: blog home page (Rmarkdown)  

`about.Rmd`: about page (Rmarkdown)  

`_posts`: folder with Rmarkdown posts

**4. distill functions**

- `create_post("name post")`
- `create_theme("name theme")`: Modify css blog theme

**5. Git/Github**

- [] Connect Github to existing project via Rstudio  
- [] 

**6. Netlify**  

- Import from github
- Change domain

**7. Basic blog workflow**

- Create new blog post in RStudio: `distill::create_post()`  
- Knit new blog post: `ctrl + shift + k`
- Commit and push: integration between RStudio and Github  

**8. Styles (CSS)** 

## Example distill blogs

- [Before I Sleep](https://milesmcbain.xyz/)
- [The Mockup](https://themockup.blog)
 

## References

- [Rstudio distill blog](https://rstudio.github.io/distill/)
